CF Registry Analysis

### 2024-02-08 Christine Chan/CF Registry/cf_registry_analysis.qmd
time varying survival models done

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(icenReg)
library(knitr)
library(eulerr)
library(broom)
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "C:/Users/timvigers/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry"
  },
  Darwin = {
    home_dir <- "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
# Import data and codebook
annual <- read.csv("./Data_Raw/CFF19_Annualized_Del1.csv",
  na.strings = c("", "N/A")
)
data_dict <- readxl::read_excel("./Data_Raw/Copy of Codes for CFFPR_2018.xlsx")
data_dict$var <- paste(data_dict$field_name, data_dict$code_value, sep = "_")
# Remove those with T1D or T2D
annual <- annual %>% arrange(eDWID, ReviewYear)
annual <- annual[!annual$cfrd_status_annual %in% c(4, 5), ]
annual$cfrd_status_annual <- factor(annual$cfrd_status_annual,
  levels = 1:3,
  labels = c("CFRD-", "CFRD-", "CFRD+")
)
# Get mutations
demogs <- read.csv("./Data_Raw/CFF19_DemogCFDiag_Del1.csv")
demogs <- demogs %>% select(eDWID, Gender, MutClass)
annual <- left_join(annual, demogs, by = join_by(eDWID))
# Variable formatting
# If A_supplement_feeding is 0, then A_feeding2 is also 0 because they are not
# on any supplemental feeding
# Include all kinds of tube feeds
annual$A_feeding2[annual$A_supplement_feeding == 0] <- 0
annual$A_feeding3[annual$A_supplement_feeding == 0] <- 0
annual$A_feeding4[annual$A_supplement_feeding == 0] <- 0
tube_fields <- c("A_feeding2", "A_feeding3", "A_feeding4")
annual$tube_feeding <-
  apply(annual[, tube_fields], 1, function(r) {
    if (all(is.na(r))) {
      return(NA)
    } else {
      return(max(as.numeric(r), na.rm = T))
    }
  })
# Liver disease
liver_fields <- c("A_hepatobiliary1_3", paste0("A_hepatobiliary2_", 1:4))
annual$liver_disease <-
  apply(annual[, liver_fields], 1, function(r) {
    if (all(is.na(r))) {
      return(NA)
    } else {
      return(max(as.numeric(r), na.rm = T))
    }
  })
# Calculate percentiles
annual$bmi <- annual$A_weight / ((annual$A_height / 100)^2)
annual$age_perc <- ifelse(annual$Age_YrEnd < 20, annual$Age_YrEnd, 20)
annual$height_perc <- sds(annual$A_height,
  age = annual$age_perc,
  sex = annual$Gender, male = "M", female = "F",
  item = "height2_20", ref = cdc.ref, type = "perc"
) * 100
annual$bmi_perc <- sds(annual$bmi,
  age = annual$age_perc,
  sex = annual$Gender, male = "M", female = "F",
  item = "bmi", ref = cdc.ref, type = "perc"
) * 100
# Format columns
annual$MutClass <- factor(annual$MutClass,
  levels = c("1-3", "4-5", "Oth", "N/A"),
  labels = c("1-3", "4-5", "Oth", "Unknown")
)
annual$NumPulmExacerbation <- cut(annual$NumPulmExacerbation,
  labels = c("0", "1", "2", ">=3"),
  breaks = c(0, 1, 2, 3, Inf), right = F
)
annual$age_group <- cut(annual$Age_YrEnd,
  breaks = c(-Inf, 10, 18, 30, Inf),
  right = F
)
annual$age_group <- relevel(annual$age_group, ref = "[10,18)")
# Bugs
bugs <- c(
  "A_pseudomonasaeruginosa", "A_fungalyeast1",
  "A_pulmonarycomplications1", "A_mycocultureresults3"
)
# Yes/No variables
yn_vars <- c(
  "A_IsOnEnzymes", "A_corticosteroids1", "A_feeding2",
  "A_Vx770", "A_VX809comb", bugs, "tube_feeding", "liver_disease"
)
annual[, yn_vars] <- lapply(annual[, yn_vars], factor,
  levels = 0:1,
  labels = c("No", "Yes")
)
annual$A_IsOnEnzymes <- relevel(annual$A_IsOnEnzymes, ref = "Yes")
# Approximate year of birth
by <- annual %>%
  mutate(birth_year = floor(ReviewYear - Age_YrEnd)) %>%
  group_by(eDWID) %>%
  count(birth_year) %>%
  group_by(eDWID) %>%
  slice_min(birth_year) %>%
  select(-n)
annual <- left_join(annual, by, by = join_by(eDWID))
# Get first year of CFRD
first_cfrd <- annual %>%
  filter(cfrd_status_annual == "CFRD+") %>%
  group_by(eDWID) %>%
  summarise(first_cfrd = min(ReviewYear))
annual <- left_join(annual, first_cfrd, by = join_by(eDWID))
# BMI percentile to categorical
annual$bmi_perc_cat <- cut(annual$bmi_perc, breaks = c(0, 10, 50, 85, Inf))
annual$bmi_perc_cat <- relevel(annual$bmi_perc_cat, ref = "(50,85]")
# FEV1 to categorical
annual$ppFEV1_cat <- cut(annual$A_FEV1_pct_predicted,
  breaks = c(0, 40, 80, 100, Inf), right = F
)
annual$ppFEV1_cat <- relevel(annual$ppFEV1_cat, ref = "[100,Inf)")
```

@@

```{r}
# List of covariates
vars <- c(
  "age_group", "Gender", "bmi_perc_cat", "MutClass", "A_IsOnEnzymes",
  "ppFEV1_cat", "tube_feeding", "NumPulmExacerbation",
  "A_pseudomonasaeruginosa", "A_fungalyeast1", "A_mycocultureresults3",
  "A_pulmonarycomplications1", "A_corticosteroids1", "cfrd_status_annual",
  "A_Vx770", "A_VX809comb", "liver_disease"
)
# Nice labels for plots and tables
labels <- list(
  cfrd_status_annual = "CFRD Status", MutClass = "Mutation class",
  Gender = "Sex", A_IsOnEnzymes = "Pancreatic enzyme use",
  ppFEV1_cat = "FEV1 percent predicted",
  tube_feeding = "Enteric feedings", liver_disease = "Liver disease",
  A_corticosteroids1 = "Use of corticosteroids",
  NumPulmExacerbation = "Admissions for PEx", age_group = "Age group",
  height_perc = "Height percentile", bmi_perc_cat = "BMI percentile",
  A_Vx770 = "Use of CFTR modulator Vx770",
  A_VX809comb = "Use of CFTR modulator Vx809 combination",
  A_pseudomonasaeruginosa = "Pseudomonas aeruginosa",
  A_fungalyeast1 = "Aspergillus (any species)",
  A_pulmonarycomplications1 = "ABPA",
  A_mycocultureresults3 = "Microorganisms in myco culture"
)
# For now, let's just assume that everyone's first CFRD+ diagnosis is correct
s <- annual %>%
  filter(
    !is.na(cfrd_status_annual),
    Age_YrEnd != 0,
    is.na(first_cfrd) | ReviewYear <= first_cfrd,
    Age_YrEnd >= 10
  ) %>%
  select(
    eDWID, ReviewYear, birth_year, Age_YrEnd,
    all_of(vars), cfrd_status_annual
  ) %>%
  rename(tstop = ReviewYear) %>%
  group_by(eDWID) %>%
  mutate(
    tstart = lag(tstop, default = birth_year[1]),
    age_at_entry = Age_YrEnd[1]
  ) %>%
  select(
    eDWID, birth_year, tstart, tstop, cfrd_status_annual,
    age_at_entry, everything()
  )
# Convert from tibble to dataframe for survival packages
s <- as.data.frame(s)
# CFRD status to numeric
s$cfrd_status_annual <- as.numeric(s$cfrd_status_annual) - 1
# Drop under 10s
s$age_group <- droplevels(s$age_group)
```

@@

```{r}
# # Whole cohort
# km_fit <- survfit(Surv(tstart, tstop, cfrd_status_annual) ~ 1,
#   data = s, cluster = eDWID
# )
# ggsurvplot(km_fit,
#   data = s, risk.table = T, cumevents = T,
#   fun = "event", xlim = c(2003, 2018), break.x.by = 1
# )
# kable(tidy(km_fit))
# # By age group
# km_fit <- survfit(Surv(tstart, tstop, cfrd_status_annual) ~ age_group,
#   data = s, cluster = eDWID
# )
# ggsurvplot(km_fit,
#   data = s, risk.table = T, cumevents = T,
#   fun = "event", xlim = c(2003, 2018), break.x.by = 1
# )
# km_table <- tidy(km_fit)
# km_table <- split.data.frame(km_table, km_table$strata)
# invisible(lapply(km_table, function(t) {
#   name <- t$strata[1]
#   t <- t %>% select(-strata)
#   kable(t, caption = name)
# }))
```

@@

```{r}
# Formula for base model
x <- c(
  "age_group", "Gender", "bmi_perc_cat", "MutClass", "A_IsOnEnzymes",
  "tube_feeding", "liver_disease",
  "ppFEV1_cat", "NumPulmExacerbation",
  "A_pulmonarycomplications1", "A_corticosteroids1"
)
y <- "Surv(tstart, tstop, cfrd_status_annual)"
f <- as.formula(paste0(y, "~", paste0(x, collapse = "+")))
cox_res <- coxph(f, data = s, cluster = eDWID)
# Plot survival
# ggsurvplot(survfit(cox_res),
#   data = s, risk.table = T, cumevents = T, fun = "event",
#   xlim = c(2003, 2018), break.x.by = 1
# )
# Forest plot and coefficients table
ggforest(cox_res, data = s)
# Diagnostics
# test.ph <- cox.zph(cox_res)
# ggcoxzph(test.ph)
# ggcoxdiagnostics(cox_res,type = "martingale")
# ggcoxdiagnostics(cox_res,type = "deviance")
# ggcoxdiagnostics(cox_res,type = "score")
# ggcoxdiagnostics(cox_res,type = "schoenfeld")
```

@@

```{r results='asis'}
s_split <- survSplit(Surv(tstart, tstop, cfrd_status_annual) ~ .,
  data = s, cut = c(2008, 2013, 2018), episode = "tgroup"
)
cox_res_split <- coxph(
  Surv(tstart, tstop, cfrd_status_annual) ~ bmi_perc_cat*strata(tgroup),
  data = s_split, cluster = eDWID
)

invisible(lapply(x, function(v) {
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "+", v, ":strata(tgroup)")
  ))
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID)
  t <- tidy(cox_res_split, exponentiate = T, conf.int = T)
  cat("\n")
  cat("####", v)
  cat("\n")
  print(kable(t, digits = 2))
  cat("\n")
  cat("\n")
  t <- t %>%
    filter(!is.na(estimate))
  p <- t %>%
    ggplot(aes(y = fct_rev(term))) +
    geom_point(aes(x = estimate), shape = 15, size = 3) +
    geom_linerange(aes(xmin = conf.low, xmax = conf.high)) +
    geom_vline(xintercept = 1, linetype = "dashed") +
    xlab("Hazard Ratio")
  cat("\n")
  print(p)
  cat("\n")
}))
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(icenReg)
library(knitr)
library(eulerr)
library(broom)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry")
```

@@

```{r}
# Import data and codebook
annual <- read.csv("./Data_Raw/CFF19_Annualized_Del1.csv",
  na.strings = c("", "N/A")
)
data_dict <- readxl::read_excel("./Data_Raw/Copy of Codes for CFFPR_2018.xlsx")
data_dict$var <- paste(data_dict$field_name, data_dict$code_value, sep = "_")
# Remove those with T1D or T2D
annual <- annual %>% arrange(eDWID, ReviewYear)
annual <- annual[!annual$cfrd_status_annual %in% c(4, 5), ]
annual$cfrd_status_annual <- factor(annual$cfrd_status_annual,
  levels = 1:3,
  labels = c("CFRD-", "CFRD-", "CFRD+")
)
# Get mutations
demogs <- read.csv("./Data_Raw/CFF19_DemogCFDiag_Del1.csv")
races <- c(
  "White", "Black or African American", "American Indian or Alaska Native",
  "Asian", "Native Hawaiian or Other Pacific ", "Some other race"
)
demogs$Race <- apply(demogs, 1, function(r) {
  w <- which(r[paste0("Race", 1:6)] == 1)
  if (length(w) > 1) {
    return("More than one race")
  } else {
    return(races[w])
  }
})
demogs$Race <- factor(demogs$Race,
  levels = c(
    "White", "American Indian or Alaska Native", "Asian",
    "Black or African American", "More than one race",
    "Native Hawaiian or Other Pacific ", "Some other race"
  ),
  labels = c(
    "White", "Other race", "Other race",
    "Black or African American", "More than one race",
    "Other race", "Other race"
  )
)
demogs$Hispanicrace <- factor(demogs$Hispanicrace,
  levels = 1:2,
  labels = c("Yes", "No")
)
demogs <- demogs %>% select(eDWID, Gender, MutClass, Race, Hispanicrace)
annual <- left_join(annual, demogs, by = join_by(eDWID))
# Variable formatting
# If A_supplement_feeding is 0, then A_feeding2 is also 0 because they are not
# on any supplemental feeding
# Include all kinds of tube feeds
annual$A_feeding2[annual$A_supplement_feeding == 0] <- 0
annual$A_feeding3[annual$A_supplement_feeding == 0] <- 0
annual$A_feeding4[annual$A_supplement_feeding == 0] <- 0
tube_fields <- c("A_feeding2", "A_feeding3", "A_feeding4")
annual$tube_feeding <-
  apply(annual[, tube_fields], 1, function(r) {
    if (all(is.na(r))) {
      return(NA)
    } else {
      return(max(as.numeric(r), na.rm = T))
    }
  })
# Liver disease
liver_fields <- c("A_hepatobiliary1_3", paste0("A_hepatobiliary2_", 1:4))
annual$liver_disease <-
  apply(annual[, liver_fields], 1, function(r) {
    if (all(is.na(r))) {
      return(NA)
    } else {
      return(max(as.numeric(r), na.rm = T))
    }
  })
# Calculate percentiles
annual$bmi <- annual$A_weight / ((annual$A_height / 100)^2)
annual$age_perc <- ifelse(annual$Age_YrEnd < 20, annual$Age_YrEnd, 20)
annual$height_perc <- sds(annual$A_height,
  age = annual$age_perc,
  sex = annual$Gender, male = "M", female = "F",
  item = "height2_20", ref = cdc.ref, type = "perc"
) * 100
annual$bmi_perc <- sds(annual$bmi,
  age = annual$age_perc,
  sex = annual$Gender, male = "M", female = "F",
  item = "bmi", ref = cdc.ref, type = "perc"
) * 100
# Format columns
annual$MutClass <- factor(annual$MutClass,
  levels = c("1-3", "4-5", "Oth", "N/A"),
  labels = c("1-3", "4-5", "Oth", "Unknown")
)
annual$NumPulmExacerbation <- cut(annual$NumPulmExacerbation,
  labels = c("0", "1", "2", ">=3"),
  breaks = c(0, 1, 2, 3, Inf), right = F
)
annual$age_group <- cut(annual$Age_YrEnd,
  breaks = c(-Inf, 10, 18, 30, Inf),
  right = F
)
annual$age_group <- relevel(annual$age_group, ref = "[10,18)")
# Bugs
bugs <- c(
  "A_pseudomonasaeruginosa", "A_fungalyeast1",
  "A_pulmonarycomplications1", "A_mycocultureresults3"
)
# Yes/No variables
yn_vars <- c(
  "A_IsOnEnzymes", "A_corticosteroids1", "A_feeding2",
  "A_Vx770", "A_VX809comb", bugs, "tube_feeding", "liver_disease"
)
annual[, yn_vars] <- lapply(annual[, yn_vars], factor,
  levels = 0:1,
  labels = c("No", "Yes")
)
annual$A_IsOnEnzymes <- relevel(annual$A_IsOnEnzymes, ref = "Yes")
# Approximate year of birth
by <- annual %>%
  mutate(birth_year = floor(ReviewYear - Age_YrEnd)) %>%
  group_by(eDWID) %>%
  count(birth_year) %>%
  group_by(eDWID) %>%
  slice_min(birth_year) %>%
  select(-n)
annual <- left_join(annual, by, by = join_by(eDWID))
# Get first year of CFRD
first_cfrd <- annual %>%
  filter(cfrd_status_annual == "CFRD+") %>%
  group_by(eDWID) %>%
  summarise(first_cfrd = min(ReviewYear))
annual <- left_join(annual, first_cfrd, by = join_by(eDWID))
# BMI percentile to categorical
annual$bmi_perc_cat <- cut(annual$bmi_perc, breaks = c(0, 10, 50, 85, Inf))
annual$bmi_perc_cat <- relevel(annual$bmi_perc_cat, ref = "(50,85]")
# FEV1 to categorical
annual$ppFEV1_cat <- cut(annual$A_FEV1_pct_predicted,
  breaks = c(0, 40, 80, 100, Inf), right = F
)
annual$ppFEV1_cat <- relevel(annual$ppFEV1_cat, ref = "[100,Inf)")
```

@@

```{r}
# List of covariates
vars <- c(
  "age_group", "Gender", "bmi_perc", "bmi_perc_cat", "MutClass", "Race",
  "Hispanicrace", "A_IsOnEnzymes", "ppFEV1_cat", "tube_feeding",
  "NumPulmExacerbation", "A_pseudomonasaeruginosa", "A_fungalyeast1",
  "A_mycocultureresults3", "A_pulmonarycomplications1", "A_corticosteroids1",
  "cfrd_status_annual", "A_Vx770", "A_VX809comb", "liver_disease"
)
# Nice labels for plots and tables
labels <- list(
  cfrd_status_annual = "CFRD Status", MutClass = "Mutation class",
  Race = "Race", Hispanicrace = "Hispanic",
  Gender = "Sex", A_IsOnEnzymes = "Pancreatic enzyme use",
  ppFEV1_cat = "FEV1 percent predicted",
  tube_feeding = "Enteric feedings", liver_disease = "Liver disease",
  A_corticosteroids1 = "Use of corticosteroids",
  NumPulmExacerbation = "Admissions for PEx", age_group = "Age group",
  height_perc = "Height percentile", bmi_perc_cat = "BMI percentile",
  A_Vx770 = "Use of CFTR modulator Vx770",
  A_VX809comb = "Use of CFTR modulator Vx809 combination",
  A_pseudomonasaeruginosa = "Pseudomonas aeruginosa",
  A_fungalyeast1 = "Aspergillus (any species)",
  A_pulmonarycomplications1 = "ABPA",
  A_mycocultureresults3 = "Microorganisms in myco culture",
  eDWID = "ID",birth_year="Birth year",tstart="Interval start",tstop="Interval stop",age_at_entry="Age at entry",Age_YrEnd="Age",bmi_perc = "BMI %ile"
)
# For now, let's just assume that everyone's first CFRD+ diagnosis is correct
s <- annual %>%
  filter(
    !is.na(cfrd_status_annual),
    Age_YrEnd != 0,
    is.na(first_cfrd) | ReviewYear <= first_cfrd,
    Age_YrEnd >= 10
  ) %>%
  select(
    eDWID, ReviewYear, birth_year, Age_YrEnd,
    all_of(vars), cfrd_status_annual
  ) %>%
  rename(tstop = ReviewYear) %>%
  group_by(eDWID) %>%
  mutate(
    tstart = lag(tstop, default = birth_year[1]),
    age_at_entry = Age_YrEnd[1]
  ) %>%
  select(
    eDWID, birth_year, tstart, tstop, cfrd_status_annual,
    age_at_entry, everything()
  )
# Convert from tibble to dataframe for survival packages
s <- as.data.frame(s)
# CFRD status to numeric
s$cfrd_status_annual <- as.numeric(s$cfrd_status_annual) - 1
# Drop under 10s
s$age_group <- droplevels(s$age_group)
# Labels
label(s) = labels[colnames(s)]
```

@@

```{r}
# Whole cohort
km_fit <- survfit(Surv(tstart, tstop, cfrd_status_annual) ~ 1,
  data = s, cluster = eDWID
)
ggsurvplot(km_fit,
  data = s, risk.table = T, cumevents = T,
  fun = "event", xlim = c(2003, 2018), break.x.by = 1
)
kable(tidy(km_fit))
# By age group
km_fit <- survfit(Surv(tstart, tstop, cfrd_status_annual) ~ age_group,
  data = s, cluster = eDWID
)
ggsurvplot(km_fit,
  data = s, risk.table = T, cumevents = T,
  fun = "event", xlim = c(2003, 2018), break.x.by = 1
)
km_table <- tidy(km_fit)
km_table <- split.data.frame(km_table, km_table$strata)
invisible(lapply(km_table, function(t) {
  name <- t$strata[1]
  t <- t %>% select(-strata)
  kable(t, caption = name)
}))
```

@@

```{r}
# Formula for base model
x <- c(
  "age_group", "Gender", "Race","Hispanicrace", "bmi_perc_cat", "MutClass", 
  "A_IsOnEnzymes", "tube_feeding", "liver_disease", "ppFEV1_cat", 
  "NumPulmExacerbation", "A_pulmonarycomplications1", "A_corticosteroids1"
)
y <- "Surv(tstart, tstop, cfrd_status_annual)"
f <- as.formula(paste0(y, "~", paste0(x, collapse = "+")))
cox_res <- coxph(f, data = s, cluster = eDWID)
# Plot survival
# ggsurvplot(survfit(cox_res),
#   data = s, risk.table = T, cumevents = T, fun = "event",
#   xlim = c(2003, 2018), break.x.by = 1
# )
# Forest plot and coefficients table
ggforest(cox_res, data = s)
# Diagnostics
test.ph <- data.frame(cox.zph(cox_res)$table)
test.ph = test.ph[rownames(test.ph) != "GLOBAL",]
# Find which variables technically violate PH assumption
time_varying = rownames(test.ph)[test.ph$p < 0.05]
# ggcoxzph(test.ph)
# ggcoxdiagnostics(cox_res,type = "martingale")
# ggcoxdiagnostics(cox_res,type = "deviance")
# ggcoxdiagnostics(cox_res,type = "score")
# ggcoxdiagnostics(cox_res,type = "schoenfeld")
```

@@

The interpretation of these models can be a little bit tricky, so here is an example using BMI percentile group and not including the other covariates in the model:

```{r}
s_split <- survSplit(Surv(tstart, tstop, cfrd_status_annual) ~ .,
  data = s, cut = c(2008, 2013, 2018), episode = "tgroup"
)
s_split$tgroup <- factor(s_split$tgroup,
  levels = 1:3, labels = c("[2003,2009)", "[2009,2014)", "[2014,2019)")
)
cox_res_split <- coxph(
  Surv(tstart, tstop, cfrd_status_annual) ~ bmi_perc_cat * strata(tgroup),
  data = s_split, cluster = eDWID
)
kable(summary(cox_res_split)$coefficients, digits = 3)
```

In the table above, the BMI reference group is the (50,85] group. So, in the years 2003 - 2008, the hazard ratio of the (0,10] BMI group was $exp(0.806)=2.238$ compared to the reference. Then, in the period of 2009 - 2013, the hazard ratio of the (0,10] BMI group was $exp(0.806+0.050)=2.354$ compared to the reference group, although this was not statistically significant. The HR for the (85,Inf] BMI group appears to increase over time, starting out at $exp(-0.511)=0.600$ in the first time period, then a statistically significant increase in the second time period to $exp(-0.511+0.282)=0.795$, with a final increase to $exp(-0.511+0.435)=0.927$ in the third period. The interpretation of the following results will follow these same formulas, and the time-varying results are shown at the bottom of each table. This report only includes variables that were statistically significant in the Cox proportional hazards test.

```{r results='asis'}
invisible(lapply(time_varying, function(v) {
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*strata(tgroup)")
  ))
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID)
  res <- summary(cox_res_split)$coefficients
  cat("\n")
  cat("####", v)
  cat("\n")
  cat("\n")
  print(kable(res, digits = 3))
  cat("\n")
}))
```
